---
title: "pagemapR"
output: html_document
---

This is an R package that provides support for [pagemap](https://larsjung.de/pagemap/) as a [htmlwidget](http://htmlwidgets.org/).

Quickly and easily add a mini map to your long rmarkdown html report.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installation

`pagemapR` is not on CRAN now (may be later), you can use `devtools` to install the latest development version.

```{r installation, eval=FALSE}
library(devtools)
install_github('swsoyee/pagemapR')
```

## Usage

It's very simple to use.

```{r usage}
pagemap::pagemap(id = "mini_map")
```

You could fix it's position on the screen and style by providing a `list` of css property.

```{r box_style}
pagemap::pagemap(id = "mini_map",
                 box_style = list(left = "5px", top = "10px"))
```

You could also customize the internal style of the mini map through the API provided by [`pagemap`](https://larsjung.de/pagemap/).

```{r customize_pagemap}
pagemap::pagemap(
  id = "mini_map",
  styles = list(
    'h1,h2,a,code' = 'rgba(0,0,0,0.10)',
    'pre' = 'rgba(0,0,0,0.06)'
  )
)
```
