---
title: "Introduction to pagemap"
author: "Wei Su"
date: "`r Sys.Date()`"
output:
  # md_document:
  #   pandoc_args: ["--wrap=preserve"]
  html_document:
    theme: flatly
    toc: true
    toc_float: true
---

<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Introduction to pagemap}
-->

```{r setup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
if (!knitr::is_html_output(excludes = "markdown")) {
  knitr::opts_chunk$set(eval = FALSE)
  logo_path <- "./vignettes/pagemap.png"
  cat("# pagemapR")
} else {
  library(devtools)
  install_github("swsoyee/pagemapR", quiet = TRUE)
  logo_path <- "./pagemap.png"
}
```

```{r logo, echo=FALSE, results='asis', eval=TRUE}
cat(
  sprintf(
    "<img src='%s' width='180' align='right' style='max-width:50%%;margin-left:20px;'>",
    logo_path
  )
)
```

<!-- badges: start -->
[![R build status](https://github.com/swsoyee/pagemapR/workflows/R-CMD-check/badge.svg)](https://github.com/swsoyee/pagemapR/actions)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/pagemap)](https://cran.r-project.org/package=pagemap)
[![metacran downloads](https://cranlogs.r-pkg.org/badges/grand-total/pagemap)](https://cran.r-project.org/package=pagemap)
<!-- badges: end -->

## Introduction

This is an R package that provides support for [`pagemap`](https://larsjung.de/pagemap/) as a [`htmlwidgets`](https://www.htmlwidgets.org/).  
Quickly and easily add a mini map to your rmarkdown `html` documents. 
See a demonstration [here](https://swsoyee.github.io/pagemapR/).

> Note: To distinguish it from the [original project `pagemap`](https://larsjung.de/pagemap/), the name of this project is `pagemapR`, but the package name is `pagemap`.


## Installation

```{r installation cran, eval=FALSE}
install.packages("pagemap")
```

Or use [`devtools`](https://www.r-project.org/nosvn/pandoc/devtools.html) to install the latest development version.

```{r installation, eval=FALSE}
# install.packages("devtools")
devtools::install_github("swsoyee/pagemapR")
```

## Usage

It's very simple to use.

```{r usage, eval=FALSE}
library(pagemap)
pagemap()
```

You could fix it's position on the screen and style by providing a `list` of css property.

```{r box_style, eval=FALSE}
pagemap(
  id = "mini_map",
  box_style = list(left = "5px", top = "10px")
)
```

You could also customize the internal style of the mini map through the API provided by [`pagemap`](https://larsjung.de/pagemap/).

```{r loading pacakge, echo=FALSE}
library(pagemap)
```

```{r customize_pagemap}
pagemap(
  id = "mini_map",
  styles = list(
    "h1,h2,a,code" = "rgba(0, 0, 0, 0.10)",
    "img" = "rgba(0, 0, 0, 0.08)",
    "pre" = "rgba(0, 0, 0, 0.04)"
  )
)
```

Or add a pagemap for your Shiny app:

```{r shiny demo, eval=FALSE}
if (interactive()) {
  shinyApp(
    ui = fluidPage(pagemapOutput("pagemap")),
    server = function(input, output) {
      output$pagemap <- renderPagemap(pagemap())
    }
  )
}
```

## Credit

This package is thanks to the work done by **Lars Jung** (<https://github.com/lrsjng>), the author of the original Javascript package `pagemap`. Also, thanks should also go to Ramnath Vaidyanathan, Kenton Russell, and RStudio, Inc. for the amazing work on create [`htmlwigets`](https://www.htmlwidgets.org/) package. The hex sticker of `pagemap`is produced by [`hexSticker`](https://github.com/GuangchuangYu/hexSticker) and [`ggplot2`](https://ggplot2.tidyverse.org/), so special thanks goes to the **Guangchuang YU** (<https://guangchuangyu.github.io>) and the `ggplot2` development team.

## Contact

You are welcome to:

* Submit suggestions and bug-reports at: 
  <https://github.com/swsoyee/pagemapR/issues>
* Send a pull request on: <https://github.com/swsoyee/pagemapR>
* Compose a friendly e-mail to: <swsoyee@gmail.com>

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/swsoyee/pagemapR/blob/master/CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
